### 2024-09-03 manuscript.tex
Add RFO to radiosonde plots
Add stable time steps plots

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/cyc_dist.pdf}
\caption{
Geographical distribution of cyclonic days in \textbf{(a)} ERA5 in years
2010--2013 (inclusive) and \textbf{(b)} ICON in model years 2021--2023 (free
running) as identified by CyTRACK, expressed as a fraction of the number of
days with cyclonic activity, defined as grid points located within a double
radius of any cyclone on a given day (UTC).
}
\label{fig:lts}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.72\textwidth]{img/theta_hur.pdf}
\caption{
Virtual potential temperature ($\theta_v$) and relative humidity (RH)
determined from radiosonde launches and co-located profiles in
ICON, ERA5 and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
The solid lines are the average calculated from the averages of every
individual voyage and station. The bands span the
16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
of the voyage and station averages.
}
\label{fig:potential-temperature}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=\textwidth]{img/cyc_stab_dist.pdf}
\caption{
Geographical distribution of \textbf{(a, b)} cyclonic days and \textbf{(b, d)}
relatively stable (LTS > 12 K) time steps in \textbf{(a, c)} ERA5 in years
2010--2013 (inclusive) and \textbf{(b, d)} ICON in model years 2021--2023 (free
running). Cyclonic days are expressed as a fraction of the number of days with
cyclonic activity, defined as grid points located within a double radius of any
cyclone on a given day (UTC), as identified by CyTRACK.
}
\label{fig:lts}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.72\textwidth]{img/theta_hur.pdf}
\caption{
Virtual potential temperature ($\theta_v$) and relative humidity (RH)
determined from radiosonde launches and co-located profiles in
ICON, ERA5 and MERRA-2 in subsets as in Fig. \ref{fig:cloud-occurrence}.
The solid lines are the average calculated from the averages of every
individual voyage and station. The bands span the
16$^\mathrm{th}$--84$^\mathrm{th}$ percentiles calculated from the distribution
of the voyage and station averages. Shown is also the relative frequency of
occurrence and the number of profiles in each subset.
}
\label{fig:potential-temperature}
\end{figure}
